---
title: "Using the champagneleowursten package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the champagneleowursten package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(champagneleowursten)
```

# Introduction

This vignette shows how to use **champagneleowursten** to:

-   define a champagne glass profile,

-   use processed weather data for cities,

-   compute the expected number of guests,

-   simulate several parties and estimate how many bottles are needed.

# Glass profile 

```{r}
glass <- GlassProfile(
  a = 12.6, b = 22.5,
  x_1 = 1.1, x_2 = 12.6, x_3 = 18.8, x_4 = 22.5,
  r_foot = 5.8, r_stem = 0.25, r_bowl = 7.5, r_rim = 7
)

radius_cone(glass, 14)          # radius at typical fill level
volume_between(glass) / 1000    # volume in litres
```

# Weather data and expected guests 

# 

The package ships a processed dataset processed_data built from OpenWeather JSON.

```{r}
data("processed_data")
head(processed_data)
```

Pick one city and build a CityWeather object :

```{r}
paris_row <- subset(processed_data, city == "Paris")[1, ]

cw <- CityWeather(
  city        = paris_row$city,
  temperature = paris_row$temperature,
  humidity    = paris_row$humidity,
  pressure    = paris_row$pressure
)

cw
lambda <- expected_lambda(cw)
lambda
```

# Simulating Parties 

We now simulate multiple parties in this city, given the glass shapes and weather-based lambda.

```{r}
set.seed(123)
res <- simulate_party(
  city_name = "Paris",
  data      = processed_data,
  glass     = glass,
  N         = 200
)

head(res)
summary(res$liters)
summary(res$bottles)
```

You can also make simple plots:

```{r}
hist(res$bottles, breaks = 10,
     main = "Distribution of bottles used",
     xlab = "Number of bottles")

boxplot(res$liters,
        main = "Distribution of total liters per party",
        ylab = "Liters")
```

Si ça marche sans erreur, voir la vignette depuis :

```{r}
browseVignettes("champagneleowursten")
```
